\section{Abstract}
Model Driven Development (MDD) can facilitate faster software development while providing consistency and protecting code integrity. Domain Specific Languages utilizing MDD can simplify the development of a specific set of repetitive tasks for a particular aspect and domain. In machine learning and data analytics projects, several tasks such as data cleaning, data adjustment, Exploratory Data Analysis (EDA), and Initial Data Analysis (IDA) are common for most projects. Although the extent and need can vary,  the code for several  aspects can be made the same to avoid repetitive code and tasks. Hence, in this project, we have developed a Domain Specific Language utilizing MDD. We have developed a Domain Specification Language (DSL) to automate Initial and Exploratory Analysis for Regression-Based Data Analytics Projects. Our project automates and writes code for Data Cleaning, Initial Analysis, and Exploratory Data Analysis. Anyone wanting to write a Data Analytics Project can use this DSL. The user can use a GUI or Text Format to define data sources and relationships among data sources. Relationships can be selected from predefined selections. The developer can select the types of analysis he or she wants such as clean/replace null values, unitary analysis, unitary plots, bi-variate regression, bi-variate plots, and r-square calculation. The DSL, by default, can/will generate code for a pre-configured (default configuration) set of tasks where the developer does not want to provide a custom list of tasks. Mandatory requirements are that our DSL will write code to clean/replace null/missing values, align data type to the majority type, r-square/adjusted r-square calculation, data normalization, unitary plot, bi-variate plot, bi-variate regression plot with the target.

%Data Analytics Regression Projects have some common tasks such as Data Cleaning, Initial Analysis, and Exploratory Data Analysis to be conducted.

